Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-11 popl24/minicat.tex
checkpoint

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed-syntax}, includes a standard boolean algebra
with $\eand$, $\eor$, $\exor$, and $\enot$ as primitives. In addition,
programs have different kinds of variables including \emph{secrets}
$\secret{\cid}{w}$, \emph{flips} $\flip{\cid}{w}$, and \emph{views}
$\view{\cid}{w}$.  Each of these variables is indexed by an ``owner''
client $\cid$ and distinguishing string $w$. So for example,
$\secret{\ttt{1}}{\ttt{"foo"}}$ is client $\ttt{1}$'s secret 
$\ttt{"foo"}$. All clients can make reference to the \emph{oracle}
through variables $\oracle{w}$- this is a form of shared randomness
that is standard in the MPC setting \cite{evans2018pragmatic}.  Each client can only
compute on their own variables in \emph{expressions} $\be$, and share
values with other clients by assignment to their views as in
$\eassign{\view{\cid}{w}}{\be}$.  A \emph{protocol} $\prog$ is a
possibly empty sequence of view assignments. We will generally omit
$\varnothing$ from example code, writing $\instr_1;\ldots;\instr_n$
instead of $\instr_1;\ldots;\instr_n;\varnothing$, and abusing notation we will
write $\prog_1;\prog_2$ to denote the concatenation of $\prog_1$
and $\prog_2$.

\begin{fpfig}[t]{$\minifed$ source code syntax.}{fig-minifed-syntax}
  {\small
    $$
    \begin{array}{rcl@{\hspace{8mm}}r}
      \multicolumn{4}{c}{b \in \{ \etrue, \efalse \},\  w \in \mathrm{String},\ \cid \in \mathrm{Clients} \subset  \mathbb{N},\ \bop \in \{ \eand, \eor, \exor \}} \\[2mm]
      \be &::=& b \mid \flip{\cid}{w} \mid \secret{\cid}{w} \mid \view{\cid}{w} \mid \oracle{w} \mid & \textit{boolean expressions}\\
      & &  \enot\ \be \mid \be\ \bop\ \be \mid \select{\be}{\be}{\be} \mid \OT{\be}{\be}{\be} \\[2mm]
      \instr &::=& \eassign{\view{\cid}{w}}{\be} & \textit{view assignments} \\[2mm]
      \prog &::=& \varnothing \mid \instr; \prog & \textit{protocols}
    \end{array}
    $$
  }
\end{fpfig}

@@

Given a variable-free boolean expression $\be$, we write $\cod{\be}$
to denote the standard interpretation of $\be$ in the binary field.
With the introduction of variables to expressions, we have two
concerns. First, we need to interpret variables with respect to a
specific memory, and second, we need to ensure that variables are used
``legally''. That is, since expressions define local computation, all
variables used in an expression must belong to the same client.  Thus,
we denote interpretation of expressions $\be$ possibly containing
variables as $\lcod{\store,\be}{\cid}$, where $\store$ associates
variables with values, and all variables must be owned by client
$\cid$. This is defined in Figure \ref{fig-minifed-interp}.

\begin{fpfig}[t]{$\minifed$ expression interpretation (T) and reduction (B) rules.}{fig-minifed-interp}
  {\small
  $$
  \begin{array}{cc}
    \begin{array}{rcl}
      \lcod{\store, \etrue}{\cid} &=& 1\\
      \lcod{\store, \efalse}{\cid} &=& 0\\
      \lcod{\store, \flip{\cid}{w}}{\cid} &=& \store(\flip{\cid}{w})\\
      \lcod{\store, \secret{\cid}{w}}{\cid} &=& \store(\secret{\cid}{w})
    \end{array} & 
    \begin{array}{rcl}
      \lcod{\store, \view{\cid}{w}}{\cid} &=& \store(\view{\cid}{w})\\
      \lcod{\store, \oracle{w}}{\cid} &=& \store(\oracle{w})\\
      \lcod{\store, \enot\ \be}{\cid} &=& \cod{\enot\ \lcod{\store,\be}{\cid}}\\
      \lcod{\store, \be_1\ \mathit{binop}\ \be_2}{\cid} &=&
      \cod{\lcod{\store,\be_1}{\cid}\ \mathit{binop}\ \lcod{\store,\be_2}{\cid}}
    \end{array}
  \end{array}
  $$
  $$
  \lcod{\store, \select{\be_1}{\be_2}{\be_3}}{\cid} =
  \begin{cases}
    \lcod{\store,\be_2}{\cid} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
    \lcod{\store,\be_3}{\cid} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
  \end{cases}%\\
      %\lcod{\store, \OT{\be_1}{\be_2}{\be_3}}{\cid} &=&
      %             \begin{cases}
      %                \lcod{\store,\be_2}{\cid'} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
      %                \lcod{\store,\be_3}{\cid'} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
      %             \end{cases}
  $$
  \vspace{1mm}

@@

Evaluation of configurations is then defined via a small-step reduction relation $\redx$,
also shown in Figure \ref{fig-minifed-interp}.
This is defined in the obvious manner for view assignments other than through
$\ttt{OT}$- however note that reduction requires that views are never reassigned. 
For view assignments through $\ttt{OT}$, we define a different reduction rule that
captures the appropriate semantics- that is, the selection bit is \emph{not} communicated
to the sender (through a view assignment), and only the selected bit is sent to the receiver:
We define $\redxs$ as the reflexive, transitive closure of $\redx$.

@@

\begin{example}[Additive Secret Sharing]
    \label{example-he}
Additive secret sharing is an MPC protocol where $k$ parties split up
their secrets into \emph{shares}, with the property that all $k$
shares are required to reconstruct the secret and any fewer reveals
nothing. Additionally, this sharing enjoys additive homomorphism. In
the binary field it is well-known that we can extend our use
of $\ttt{xor}$ and flips to generate an arbitrary number of shares
with additive homomorphism.

For example, to generate shares for three-party additive sharing,
clients 1,2, and 3 can break up and distribute their shares to
each other as follows:
{\small
\begin{verbatimtab}
     v[2,"s1"] := flip[1,"1"] xor flip[1,"s1"] xor s[1,"1"];
     v[3,"s1"] := flip[1,"1"];
     v[1,"s2"] := flip[2,"1"] xor flip[2,"s2"] xor s[2,"1"];
     v[3,"s2"] := flip[2,"1"];
     v[1,"s3"] := flip[3,"1"] xor flip[3,"s3"] xor s[3,"1"];
     v[2,"s3"] := flip[3,"1"] \end{verbatimtab}
}
Then, assuming that party 0 is a ``public'' client, each party sums
its own shares, and then the sum of the sum of shares is revealed
in the output view $\vx{0}{output}$. By additive homomorphism of
$\ttt{xor}$, this output is the sum of the 3 secrets.
{\small
\begin{verbatimtab}
     v[0,"ss1"] := v[1,"s2"] xor v[1,"s3"] xor flip[1,"s1"];
     v[0,"ss2"] := v[2,"s1"] xor v[2,"s3"] xor flip[2,"s2"];
     v[0,"ss3"] := v[3,"s1"] xor v[3,"s2"] xor flip[3,"s3"];
     v[0,"output"] := v[0,"ss1"] xor v[0,"ss2"] xor v[0,"ss3"] \end{verbatimtab}
}
We note that, as for MPC protocols generally, the notion of
``secrecy'' here is subtle and not the same as for encryption as in
Example \ref{example-otp}, particularly when the threat model allows
protocol participants to be corrupt. For example, suppose that $1 \in C$, and
$\sx{1}{1}$ is $1$, and after running the protocol suppose that
$\vx{0}{output}$ is 0. Then the adversary knows that 2 and 3's secrets
are either 1 and 0, or 0 and 1, with 50/50 probability, and definitely
neither 0 and 0, nor 1 and 1. 
\end{example}

>>>>

\subsection{Syntax} The syntax of $\minifed$, defined in
Figure \ref{fig-minifed}, includes a standard boolean algebra
with $\eand$, $\eor$, $\exor$, and $\enot$ as primitives. In addition,
programs have different kinds of variables including \emph{secrets}
$\secret{\cid}{w}$, \emph{flips} $\flip{\cid}{w}$, and \emph{views}
$\view{\cid}{w}$.  Each of these variables is indexed by an ``owner''
client $\cid$ and distinguishing string $w$. So for example,
$\secret{\ttt{1}}{\ttt{"foo"}}$ is client $\ttt{1}$'s secret 
$\ttt{"foo"}$. All clients can make reference to the \emph{oracle}
through variables $\oracle{w}$- this is a form of shared randomness
that is standard in the MPC setting \cite{evans2018pragmatic}.  Each client can only
compute on their own variables in \emph{expressions} $\be$, and share
values with other clients by assignment to their views as in
$\eassign{\view{\cid}{w}}{\be}$.  A \emph{protocol} $\prog$ is a
possibly empty sequence of view assignments. We will generally omit
$\varnothing$ from example code, writing $\instr_1;\ldots;\instr_n$
instead of $\instr_1;\ldots;\instr_n;\varnothing$, and abusing notation we will
write $\prog_1;\prog_2$ to denote the concatenation of $\prog_1$
and $\prog_2$.

@@

Given a variable-free boolean expression $\be$, we write $\cod{\be}$
to denote the standard interpretation of $\be$ in the binary field.
With the introduction of variables to expressions, we have two
concerns. First, we need to interpret variables with respect to a
specific memory, and second, we need to ensure that variables are used
``legally''. That is, since expressions define local computation, all
variables used in an expression must belong to the same client.  Thus,
we denote interpretation of expressions $\be$ possibly containing
variables as $\lcod{\store,\be}{\cid}$, where $\store$ associates
variables with values, and all variables must be owned by client
$\cid$. This is defined in Figure \ref{fig-minifed}.

\begin{fpfig}[t]{$\minifed$ syntax (T), expression interpretation (M),  and reduction (B) rules.}{fig-minifed}
  {\small
    $$
    \begin{array}{rcl@{\hspace{8mm}}r}
      \multicolumn{4}{c}{b \in \{ \etrue, \efalse \},\  w \in \mathrm{String},\ \cid \in \mathrm{Clients} \subset  \mathbb{N},\ \bop \in \{ \eand, \eor, \exor \}} \\[2mm]
      \be &::=& b \mid \flip{\cid}{w} \mid \secret{\cid}{w} \mid \view{\cid}{w} \mid \oracle{w} \mid & \textit{boolean expressions}\\
      & &  \enot\ \be \mid \be\ \bop\ \be \mid \select{\be}{\be}{\be} \mid \OT{\be}{\be}{\be} \\[2mm]
      \instr &::=& \eassign{\view{\cid}{w}}{\be} & \textit{view assignments} \\[2mm]
      \prog &::=& \varnothing \mid \instr; \prog & \textit{protocols}
    \end{array}
    $$
  }

  {\small
  $$
  \begin{array}{cc}
    \begin{array}{rcl}
      \lcod{\store, \etrue}{\cid} &=& 1\\
      \lcod{\store, \efalse}{\cid} &=& 0\\
      \lcod{\store, \flip{\cid}{w}}{\cid} &=& \store(\flip{\cid}{w})\\
      \lcod{\store, \secret{\cid}{w}}{\cid} &=& \store(\secret{\cid}{w})
    \end{array} & 
    \begin{array}{rcl}
      \lcod{\store, \view{\cid}{w}}{\cid} &=& \store(\view{\cid}{w})\\
      \lcod{\store, \oracle{w}}{\cid} &=& \store(\oracle{w})\\
      \lcod{\store, \enot\ \be}{\cid} &=& \cod{\enot\ \lcod{\store,\be}{\cid}}\\
      \lcod{\store, \be_1\ \mathit{binop}\ \be_2}{\cid} &=&
      \cod{\lcod{\store,\be_1}{\cid}\ \mathit{binop}\ \lcod{\store,\be_2}{\cid}}
    \end{array}
  \end{array}
  $$
  $$
  \lcod{\store, \select{\be_1}{\be_2}{\be_3}}{\cid} =
  \begin{cases}
    \lcod{\store,\be_2}{\cid} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
    \lcod{\store,\be_3}{\cid} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
  \end{cases}%\\
      %\lcod{\store, \OT{\be_1}{\be_2}{\be_3}}{\cid} &=&
      %             \begin{cases}
      %                \lcod{\store,\be_2}{\cid'} & \text{if\ } \lcod{\store,\be_1}{\cid}\\
      %                \lcod{\store,\be_3}{\cid'} & \text{if\ } \neg\lcod{\store,\be_1}{\cid}
      %             \end{cases}
  $$
  \vspace{1mm}

@@

Evaluation of configurations is then defined via a small-step reduction relation $\redx$,
also shown in Figure \ref{fig-minifed}.
This is defined in the obvious manner for view assignments other than through
$\ttt{OT}$- however note that reduction requires that views are never reassigned. 
For view assignments through $\ttt{OT}$, we define a different reduction rule that
captures the appropriate semantics- that is, the selection bit is \emph{not} communicated
to the sender (through a view assignment), and only the selected bit is sent to the receiver:
We define $\redxs$ as the reflexive, transitive closure of $\redx$.

@@
